Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-07 thesis/paper.tex
external val

\smallskip \noindent
\textbf{External validity  }

@@

2
Counteracted: 
Triangulation by checking both code, documentation and interviewing.

Remaining: 
Only interviewing architects. Maybe business ppl need to be invited to find intents.
Not interviewing partners

>>>>

\smallskip \noindent
\textbf{External validity  } The results of our study should be highly generalisable similar studies conducted on any type of APIs, since the evolution of the API has largely been driven by software-related factors. Our study should be of special interest to researchers studying platform or embedded APIs. The fact that the results of the study are presented in a structured way, by relating them to existing software evolution theories, should further increase the generalisability of our study.

@@
